%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Jason Dominguez} \\ \vspace{1pt}
    \small 07539570493 $|$ \href{mailto:jasonjdominguez99@gmail.com}{\underline{jasonjdominguez99@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/jasonjdominguez99/}{\underline{linkedin.com/in/jasonjdominguez99}} $|$
    \href{https://github.com/jasonjdominguez99}{\underline{github.com/jasonjdominguez99}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Manchester}{Manchester, UK}
      {Cmp Sci. PhD in Generative Deep Learning for Music Composition}{Sep. 2021 -- Mar. 2025}
    \resumeSubheading
      {University of Manchester}{Manchester, UK}
      {1\textsuperscript{st} class MPhys in Physics (82\%)}{Sep. 2017 -- June 2021}
    \resumeSubheading
      {Thomas Hardye Sixth Form}{Dorchester, UK}
      {A levels: Maths (A*), Physics (A*), Music Tech (A), AS Further maths (A)}{Sep. 2015 -- June 2017}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python (4+ years), C/C++ (4+ years), SQL/MySQL (Beginner), MATLAB (2+ years)} \\
     \textbf{Deep learning frameworks}{: TensorFlow, Keras, PyTorch} \\
     \textbf{Libraries}{: Pandas, NumPy, Matplotlib, Scikit-Learn, OpenCV} \\
    }}
 \end{itemize}
 
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Programming And Machine Learning In My Degree}{Sep. 2017 -- Present}
      {University of Manchester}{Manchester, UK}
      \resumeItemListStart
        \resumeItem{Achieved 91\% in “Machine Learning and Optimization” course from the Electrical and Electronic Engineering department, with coursework on creating neural networks in Python and MATLAB.}
        \resumeItem{Familiarity with implementing linear regression, logistic regression, SVM, Fisher LDA, PCA, decision trees and naive Bayes models.}
        \resumeItem{Took “Object-oriented programming in C++” module to enhance my coding skills. My final project included creating a chess game from scratch using advanced C++ features, including polymorphism, smart pointers, move semantics and class inheritance.}
        \resumeItem{I took a Python and C++ module (80\%) and I use python frequently for data analysis for experiments.}
        \resumeItem{Achieved a high first in a statistics module, covering topics such as the central limit theorem, Bayesian statistics and Gaussian, Poisson and Binomial distributions.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Deep Learning Specialization}{Jun. 2020 -- Sep. 2020}
      {deeplearning.ai}{Coursera}
      \resumeItemListStart
        \resumeItem{I completed three online deep learning specialization consisting of 15 courses. These courses involved implementing algorithms from current research to different applications, such as image classification and generative deep learning.}
        \resumeItem{I gained familiarity with Keras and Tensorflow in Python, to create train and test VAEs, GANs and RNNs. }
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Can Machine Learning Identify Liquid Crystal Phases} $|$ \emph{Python, CNNs, YOLO, Keras}}{Sept. 2020 -- Present}
          \resumeItemListStart
            \resumeItem{I am applying machine learning algorithms, CNNs and Inception networks, to identify different liquid crystal phases from the structure of their textures.}
            \resumeItem{I also extended this to apply trained networks to videos to detect liquid crystal phase transitions.}
            \resumeItem{Additionally gained familiarity with leading object detection algorithm, YOLO, to detect nematic defects textures.}
            \resumeItem{This is novel in the field of soft matter physics, so we plan to publish two papers on this machine learning application in the coming months.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------Hobbies-----------
\section{Non-academic interests}
\resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Music} $|$ \emph{Drums, Guitar, Vocals, original compositions}}{}
          \resumeItemListStart
            \resumeItem{I am a musician, with 10 years experience playing drums and 5+ years experience playing guitar, bass, Canarian timple and singing.}
            \resumeItem{I achieved a distinction in grade 5 drumming and a merit in grade 2 singing.}
            \resumeItem{In my spare time I compose original music both by myself and as part of my band, a newly formed Indie rock band based in Manchester.}
            \resumeItem{I have contributed to original songs which have been semi-professionally recorded. Currently, original songs which I contributed to when I was 16 years old are available on Spotify - Band: The Salt, EP: Not the plan.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-------------------------------------------
%
\end{document}
